Supplement 1

### 2020-09-08 paper/supplement-1.Rmd
changes to example 1. stole Nick's idea from the main text of the paper.

@@

MCAR refers to missingness that is unrelated to any observed or
unobserved data. Missing Australian Football player ratings could be
considered MCAR, if the missing ratings are not systematically related
to other variables. MAR is where missingness is related to some observed
data. Data MAR could arise if\... \^\^Rob's out on the full
example\--players who are injured are less likely to fill out wellness
surveys than those who are fully fit.\^\^. MNAR is when missingness is
related to something unobservable. For example, data MNAR could arise
when, if studying doping, a player was to remove their head and body
hair, to avoid providing a hair sample for testing
[\[4\]](https://www.zotero.org/google-docs/?4Ildjf). In this case, data
is missing (the hair sample), and this information is not captured by
any other variable that was collected (hair length was not recorded).

>>>>

There are three broad categorisations describing why data can be 
missing: Missing Completely at Random (MCAR), Missing at Random (MAR), 
and Missing Not at Random (MNAR). These categorisations help describe 
whether the missingness occurs by chance (MCAR), due to some observed 
variable (MAR) or an unobserved variable (MNAR), with MCAR being 
the least harmful, and MAR and MNAR biased. Here, we provide an example 
of data MAR, MCAR and MNAR.

Data MCAR could occur if an Australian Football data collector was taking 
lunch during the third quarter of a match, resulting in data not being 
recorded for this time period. Data is MCAR, because the missings are 
not systematically related to other variables.

Data may be considered MAR is where missingness is related to some observed
data. Data MAR could arise if\... \^\^Rob's out on the full
example\--players who are injured are less likely to fill out wellness
surveys than those who are fully fit.\^\^.

MNAR is when missingness is
related to something unobservable. For example, data MNAR could arise
when, if studying doping, a player was to remove their head and body
hair, to avoid providing a hair sample for testing
[\[4\]](https://www.zotero.org/google-docs/?4Ildjf). In this case, data
is missing (the hair sample), and this information is not captured by
any other variable that was collected (hair length was not recorded).

# Older ideas

@@
